### 2021-04-22 paper/ase21/eval.tex
[ASE21] Applied comments

We measured the performance of $\tool$ with the worklist iteration number
and the analysis time.  For each version of ECMAScript,
$\tool$ took \inred{137.3} seconds with \inred{301.6}K iterations of
the worklist algorithm on average.  The average analysis time consists of \inred{8.0} seconds
for the specification extraction (\stextsf{extract}),
\inred{128.5} seconds for the type analysis (\stextsf{analyze}), and
\inred{0.8} seconds for the bug detection (\stextsf{detect}).

@@

To understand the severity of the detected true bugs, we extended $\tool$ to
automatically extract when they are created and resolved in the ECMAScript
official repository.  A bug is \textit{created} when it exists
in a specific version but does not exist in its previous version, and
a bug is \textit{resolved} vice versa. The \textit{Time to Live (TTL)} of a bug denotes
how many days the bug lasts.  Figure~\ref{fig:ttl} illustrates the TTLs of true bugs;
Figure~\ref{fig:ttl}(a) depicts the TTLs sorted by creation time and
Figure~\ref{fig:ttl}(b) depicts the histogram of the TTLs in a logarithmic scale.
Among \inred{93} true bugs, \inred{48} bugs are \textit{inherited},
which means that they are created before 2018,
and \inred{14} bugs still exist in the latest ECMAScript, which are newly detected by $\tool$.
We discuss the details of \inred{14} newly found bugs in Section~\ref{sec:new-bug}.
Even though we assume that \inred{48} inherited bugs are created on January 1, 2018,
the average TTL is \inred{414.5} and the maximum TTL is \inred{1,164}.
All the bugs with the maximum TTL are inherited ones and they are all newly detected.

@@

For performance comparison, Figure~\ref{fig:performance-compare} presents the
iterations and analysis time without and with refinement.
Figures~\ref{fig:performance-compare}(a) and
\ref{fig:performance-compare}(c) are histograms of the iterations and analysis
time, respectively, and Figures~\ref{fig:performance-compare}(b) and
\ref{fig:performance-compare}(d) are scatter charts for their ratios.
Without refinement, the type analysis took \inred{91.9} seconds with \inred{261.5}K
iterations on average.  For each version, the number of iterations is increased
at least \inred{0.99}x, at most \inred{1.36}x, and \inred{1.16}x on average, and
the analysis time is increased at least \inred{1.05}x, at most \inred{1.99}x,
and \inred{1.41}x on average.

Table~\ref{table:precision} shows the analysis precision without refinement,
with refinement, and their difference.  The refinement improved the analysis
precision from \inred{33.0}\% to \inred{59.2}\% by removing \inred{122}
false-positive bugs and detecting \inred{one} more true bug.  Among six
bug kinds, the most significant improvement is for non-numeric
operand bugs (\stextsf{NoNumber}) from \inred{3.1}\% to \inred{33.3}\%
by removing \inred{59} false-positive bugs.  The refinement technique
successfully prunes out non-numeric values for numeric types.
The refinement also significantly increased the analysis precision for unknown
variable bugs (\stextsf{UnknownVar}) and assertion failures
(\stextsf{Assertion}) by removing \inred{29} and \inred{25} false-positive bugs, respectively.
Because $\tool$ can precisely analyze callees of function invocations
without refinement, we found no improvement for missing
parameter bugs (\stextsf{MissingParam}).

@@

Among \inred{93} true bugs detected by $\tool$, \inred{14} are newly
detected and still exist in the latest version of ECMAScript.
Table~\ref{table:new-bug} summarizes the bugs, their
related JavaScript language features, and their TTLs.
Except for two bugs in ES12-8, all bugs were introduced in the initial
commit of the open development on September 22, 2015.
Thus, 12 newly detected bugs last for 1,966 days until March 9, 2021.
The two bugs in ES12-8 were created when a contributor introduced
the prefixes \textbf{?} and \textbf{!} on December 16, 2015, and they last for 1,910 days.
We reported the newly detected bugs to TC39, and all of them were
confirmed by the committee and will be fixed in ECMAScript 2022 (ES13).

>>>>

We measured the performance of $\tool$ with the worklist iteration number
and the analysis time.  For each version of ECMAScript,
$\tool$ took \inred{137.3} seconds with \inred{301.6}K iterations of
the worklist algorithm on average.  The average analysis time consists of \inred{8.0} seconds
for the specification extraction (\stextsf{extract}),
\inred{128.5} seconds for the type analysis (\stextsf{analyze}), and
\inred{0.8} seconds for the bug detection (\stextsf{detect}).
Therefore, We believe that $\tool$ is enough to be as part of continuous
integration pipeline in open development process of ECMAScript.

@@

To understand the impact of the detected true bugs, we extended $\tool$ to
automatically extract when they are created and resolved in the ECMAScript
official repository.  A bug is \textit{created} when it exists
in a specific version but does not exist in its previous version, and
a bug is \textit{resolved} vice versa. The \textit{Time to Live (TTL)} of a bug denotes
the number of days between the created date and the resolved date.
Figure~\ref{fig:ttl} illustrates the TTLs of true bugs;
Figure~\ref{fig:ttl}(a) depicts the TTLs sorted by creation time and
Figure~\ref{fig:ttl}(b) depicts the histogram of the TTLs in a logarithmic scale.
Among \inred{93} true bugs, \inred{48} bugs are \textit{inherited},
which means that they are created before 2018,
and \inred{14} bugs still exist in the latest ECMAScript, which are newly detected by $\tool$.
We discuss the details of \inred{14} newly found bugs in Section~\ref{sec:new-bug}.
Even though we assume that \inred{48} inherited bugs are created on January 1, 2018,
the average TTL is \inred{414.5} and the maximum TTL is \inred{1,164}.
All the bugs with the maximum TTL are inherited ones and they are all newly detected.

@@

For performance comparison, Figure~\ref{fig:performance-compare} presents the
iterations and analysis time without and with refinement.
Figures~\ref{fig:performance-compare}(a) and
\ref{fig:performance-compare}(c) are histograms of the iterations and analysis
time, respectively, and Figures~\ref{fig:performance-compare}(b) and
\ref{fig:performance-compare}(d) are scatter charts for their ratios.
Without refinement, the type analysis took \inred{91.9} seconds with \inred{261.5}K
iterations on average.  After applying refinement, the number of iterations is increased
at least \inred{0.99}x, at most \inred{1.36}x, and \inred{1.16}x on average, and
the analysis time is increased at least \inred{1.05}x, at most \inred{1.99}x,
and \inred{1.41}x on average.

Table~\ref{table:precision} shows the analysis precision without refinement,
with refinement, and their difference.  The refinement improved the analysis
precision from \inred{33.0}\% to \inred{59.2}\% by removing \inred{122}
false-positive bugs and detecting \inred{one} more true bug.  Among six
bug kinds, the most significant improvement is for non-numeric
operand bugs (\stextsf{NoNumber}) from \inred{3.1}\% to \inred{33.3}\%
by removing \inred{59} false-positive bugs.  The refinement technique
successfully prunes out non-numeric values for numeric types.
The refinement significantly increased the analysis precision also for unknown
variable bugs (\stextsf{UnknownVar}) and assertion failures
(\stextsf{Assertion}) by removing \inred{29} and \inred{25} false-positive bugs, respectively.
Because $\tool$ can precisely analyze callees of function invocations
without refinement, we found no improvement for missing
parameter bugs (\stextsf{MissingParam}).

@@

Among \inred{93} true bugs detected by $\tool$, \inred{14} are newly
detected and still exist in the latest version of ECMAScript.
Table~\ref{table:new-bug} summarizes the bugs, their
related JavaScript language features, and their TTLs.
Except for two bugs in ES12-8, all bugs were introduced in the initial
commit of the open development on September 22, 2015.
Thus, 12 newly detected bugs last for 1,996 days until March 9, 2021.
The two bugs in ES12-8 were created when a contributor introduced
the prefixes \textbf{?} and \textbf{!} on December 16, 2015, and they last for 1,910 days.
We reported the newly detected bugs to TC39, and all of them were
confirmed by the committee and will be fixed in ECMAScript 2022 (ES13).

### 2021-04-22 paper/ase21/intro.tex
[ASE21] Applied comments

To alleviate this problem, we propose a tool $\tool$, a \textbf{J}avaScript
\textbf{S}pecification \textbf{T}ype \textbf{A}nalyzer using
\textbf{R}efinement. In order to perform a \textit{type analysis} on ECMAScript
to statically detect type-related specification bugs automatically,
the main challenge is that ECMAScript describes abstract algorithms in
a natural language, English. While researchers~\cite{lambdajs, jscert, kjs}
have formally defined various JavaScript semantics for different
versions of ECMAScript by hand, manual formalization is not suitable for
automatically detecting bugs in rapidly evolving JavaScript specifications. 
Thus, recent approaches in diverse fields such as system architectures~\cite{x86, arm},
network protocols~\cite{basespec}, and language specifications~\cite{spectest, javadoc}
have utilized information directly extracted from specifications written in a natural language
to lessen such burdens.
Among them, $\jiset$~\cite{jiset} compiles ECMAScript abstract algorithms written in
a structured natural language to functions in $\ires$, an untyped
intermediate representation for ECMAScript.
Therefore, $\tool$ can handle JavaScript specifications mechanically using $\jiset$.

For mechanized JavaScript specifications by $\jiset$, $\tool$ performs
a type analysis of compiled functions using \textit{specification types}
defined in ECMAScript. ECMAScript contains not only JavaScript
language types but also specification types such as abstract syntax
trees (ASTs), internal list-like structures, and internal records
including environments, completions, and property descriptors. We
define their type hierarchies and fields based on the type-related
tables in ECMAScript and automatically extracted syntax-directed algorithms.
Using such type information, $\tool$ performs a type analysis and detects specification bugs using
a \textit{bug detector} consisting of four checkers: 1) a reference
checker, 2) an arity checker, 3) an assertion checker, and 4) an operand checker.
$\tool$ also uses a \textit{condition-based refinement} for type
analysis, which prunes out infeasible parts in abstract states by using conditions
of assertions and branches to improve the precision of type analysis.
We evaluated $\tool$ with all \inred{864} versions in the official
ECMAScript repository for the recent three years from 2018 to 2021.
The experiments showed that the refinement technique could reduce the number of
false-positive bugs caused by spurious types inferred by imprecise type analysis.

>>>>

To alleviate this problem, we propose a novel tool $\tool$, a \textbf{J}avaScript
\textbf{S}pecification \textbf{T}ype \textbf{A}nalyzer using
\textbf{R}efinement. In order to perform a \textit{type analysis} on ECMAScript
to statically detect type-related specification bugs automatically,
the main challenge is that ECMAScript describes abstract algorithms in
a natural language, English. While researchers~\cite{lambdajs, jscert, kjs}
have formally defined various JavaScript semantics for different
versions of ECMAScript by hand, manual formalization is not suitable for
automatically detecting bugs in rapidly evolving JavaScript specifications. 
Thus, recent approaches in diverse fields such as system architectures~\cite{x86, arm},
network protocols~\cite{basespec}, and language specifications~\cite{spectest, javadoc}
have utilized information directly extracted from specifications written in a natural language
to lessen such burdens.
Among them, $\jiset$~\cite{jiset} compiles ECMAScript abstract algorithms written in
a structured natural language to functions in $\ires$, an untyped
intermediate representation for ECMAScript.
Therefore, $\tool$ leverages $\jiset$ to mechanically handle JavaScript specifications.

For mechanized JavaScript specifications by $\jiset$, $\tool$ performs
a type analysis of compiled functions using \textit{specification types}
defined in ECMAScript. ECMAScript contains not only JavaScript
language types but also specification types such as abstract syntax
trees (ASTs), internal list-like structures, and internal records
including environments, completions, and property descriptors. We
define their type hierarchies based on subtype relations and fields for record and AST types.
Using such type information, $\tool$ performs a type analysis and detects specification bugs using
a \textit{bug detector} consisting of four checkers: 1) a reference
checker, 2) an arity checker, 3) an assertion checker, and 4) an operand checker.
$\tool$ also uses a \textit{condition-based refinement} for type
analysis, which prunes out infeasible parts in abstract states by using conditions
of assertions and branches to improve the precision of type analysis.
We evaluated $\tool$ with all \inred{864} versions in the official
ECMAScript repository for the recent three years from 2018 to 2021.
The experiments showed that the refinement technique could reduce the number of
false-positive bugs caused by spurious types inferred by imprecise type analysis.

### 2021-04-22 paper/ase21/overview.tex
[ASE21] Applied comments

\paragraph{Types}
$\tool$ represents three kinds of specification types.
First, because ASTs are values in abstract algorithms, 
they can be stored in variables and passed as function arguments.
For ASTs, we use their production names as their
types and automatically link their corresponding syntax-directed algorithms as their fields.
Second, ECMAScript supports various record types and fields
whose possible values are defined in their corresponding tables.
For example, ``Table 9: Completion Record Fields'' in the latest
ECMAScript describes the fields of the completion records.
% The newest version contains tens of tables for record types, and they are backward compatible in general.
Thus, we manually model the fields of record types based on the tables
in the latest version and use them in a type analysis.
Third, for list-like structures, we define the empty list type
$\clist{}$ and parametric list types $\clist{\tau}$.

@@

$\tool$ performs a type analysis with flow-sensitivity and
type-sensitivity for arguments.
Each function is split into multiple flow- and type-sensitive views, and an
abstract state stores mapping from views to corresponding abstract environments.
To handle views separately, we use a worklist algorithm.
The type analyzer consists of two sub-modules: an \textit{analysis initializer} and an
\textit{abstract transfer}.

@@

\paragraph{Abstract Transfer} For each iteration, the abstract transfer gets a
specific view from the worklist and updates the abstract environments of the next
views based on the abstract semantics.  It adds the next views to the worklist if
it changes their abstract environments, and the iteration finishes when
the worklist becomes empty.  To increase the analysis precision, we
perform a condition-based refinement for an abstract environment when the current
control point is a branch or an assertion as described in Section~\ref{sec:refine}.

@@

\paragraph{Arity Checker} The program finally calls \jscode{f} with an argument \jscode{true}.
During the initialization of the function call, the \textbf{IteratorBindingInitialization}
algorithm executes with additional parameters \textit{iteratorRecord} and
\textit{environment} to assign argument values to parameters.
However, a contributor missed passing additional arguments to them on line 2 in
\textbf{IteratorBindingInitialization} of \textit{ArrowParameters} on September 6, 2018.
It caused an arity mismatch bug, which existed for 533 days until another
contributor fixed it on February 20, 2020. The arity checker can detect such arity mismatches.

@@

In the remainder of this paper, we explain the details of how to perform type
analysis for $\ires$ functions and how to increase the analysis precision using
the condition-based refinement (Section~\ref{sec:analyzer}) and how to detect
type-related specification bugs (Section~\ref{sec:checker}).  After we evaluate $\tool$
(Section~\ref{sec:eval}), we discuss related work (Section~\ref{sec:related}),
and conclude (Section~\ref{sec:conclusion}).

>>>>

\paragraph{Types}
In addition to JavaScript types,
$\tool$ represents three kinds of specification types.
First, because ASTs are values in abstract algorithms, 
they can be stored in variables and passed as function arguments.
For ASTs, we use their production names as their
types and automatically link their corresponding syntax-directed algorithms as their fields.
Second, ECMAScript supports various record types and fields
whose possible values are defined in their corresponding tables.
For example, ``Table 9: Completion Record Fields'' in the latest
ECMAScript describes the fields of the completion records.
% The newest version contains tens of tables for record types, and they are backward compatible in general.
Thus, we manually model the fields of record types based on the tables
in the latest version and use them in a type analysis.
Third, for list-like structures, we define the empty list type
$\clist{}$ and parametric list types $\clist{\tau}$.

@@

$\tool$ performs a type analysis with flow-sensitivity and
type-sensitivity for arguments.
Each function is split into multiple flow- and type-sensitive views, and an
abstract state stores mapping from views to corresponding abstract environments.
To handle views separately, we use a worklist algorithm.
The type analyzer consists of two sub-modules: an \textit{analysis initializer} and an
\textit{abstract transfer function}.

@@

\paragraph{Abstract Transfer Function} For each iteration, the abstract transfer function gets a
specific view from the worklist and updates the abstract environments of the next
views based on the abstract semantics.  It adds the next views to the worklist if
it changes their abstract environments, and the iteration finishes when
the worklist becomes empty.  To increase the analysis precision, we
perform a condition-based refinement for an abstract environment when the current
control point is a branch or an assertion as described in Section~\ref{sec:refine}.

@@

\paragraph{Arity Checker} The program finally calls \jscode{f} with an argument \jscode{true}.
During the initialization of the function call, the \textbf{IteratorBindingInitialization}
algorithm is executed with additional parameters \textit{iteratorRecord} and
\textit{environment} to assign argument values to parameters.
However, a contributor missed passing additional arguments to them on line 2 in
\textbf{IteratorBindingInitialization} of \textit{ArrowParameters} on September 6, 2018.
It caused an arity mismatch bug, which existed for 533 days until another
contributor fixed it on February 20, 2020. The arity checker can detect such arity mismatches.

@@

In the remainder of this paper, we explain the details of how to perform type
analysis for $\ires$ functions and how to increase the analysis precision using
the condition-based refinement (Section~\ref{sec:analyzer}) and how to detect
type-related specification bugs (Section~\ref{sec:checker}).  After we evaluate $\tool$
(Section~\ref{sec:eval}), we discuss related work (Section~\ref{sec:related})
and conclude (Section~\ref{sec:conclusion}).

### 2021-04-22 paper/ase21/related.tex
[ASE21] Applied comments

\paragraph{JavaScript Tools}
ECMAScript is the standard language specification for JavaScript maintained by
the Ecma Technical Committee 39 (TC39).  In late 2014, the committee announced
its plan to release ECMAScript annually and adopt the open development process
to quickly adapt to evolving development environments.  Various JavaScript engines such
as Google V8~\cite{v8}, GraalJS~\cite{graaljs}, QuickJS~\cite{qjs}, and Moddable
XS~\cite{moddable} should conform to the syntax and semantics described in
annually updated ECMAScript.  Beyond JavaScript engines, diverse
research projects use JavaScript specifications.  The main research direction
has been static analyzers such as JSAI~\cite{jsai}, SAFE~\cite{safe},
TAJS~\cite{tajs}, and WALA~\cite{wala} based on the abstract interpretation
framework~\cite{ai1977, ai1992} with their own analysis techniques.
They defined abstract semantics of the JavaScript semantics described in ECMAScript to statically
analyze JavaScript programs in a finite time.
Chargu{\'e}raud et al.~\cite{jsexplain} presented JSExplain, a debugger for JavaScript, by
implementing a reference interpreter in OCaml following the algorithm steps in ECMAScript closely.
For a given JavaScript program, the debugger interactively produces execution traces
investigated in a browser, with an interface that displays the
JavaScript code and the interpreter's state.
Fragoso Santos et al.~\cite{javert} introduced JaVerT, a JavaScript verification toolchain, based
on the separation logic with an intermediate goto language JSIL.
JaVerT 2.0~\cite{javert2} extends it to support compositional symbolic execution
for JavaScript based on bi-abduction.  However, because all of them manually handle
ECMAScript with their own intermediate representations, most of them still 
target ES5.1 released in 2011 instead of the latest one.

\paragraph{Mechanized Specification Extraction}
Researchers in various application domains have extracted mechanized specifications from
specifications written in natural languages to handle the contents in the specifications automatically.
For system architectures, researchers utilized Natural
Language Processing (NLP) and Machine Learning (ML) techniques to extract formal semantics
of small-sized low-level assembly languages for x86~\cite{x86} and ARM~\cite{arm}.
For Java API functions, Zhai et al.~\cite{javadoc} presented a
technique to automatically extract models from their documentation using NLP techniques.
For the JavaScript programming language, Park et al.~\cite{jiset}
presented $\jiset$, a tool that extracts a mechanized specification from ECMAScript.
While all the previous JavaScript formal semantics~\cite{lambdajs, jscert,
kjs} were manually defined, $\jiset$ automatically extracts formal semantics directly from ECMAScript.
We utilized $\jiset$ to analyze 864 ECMAScript versions via $\tool$.

\paragraph{Specification-based Testing}
Recently, researchers have utilized specifications to test their implementations.
For network protocols, Kim et al.~\cite{basespec} proposed a novel approach named
\textsc{BaseSpec}, which extracts message structures from tables in cellular
specifications for L3 protocols to perform comparative analysis of baseband software.
Schumi and Sun~\cite{spectest} presented SpecTest, which utilized an
executable language semantics to perform fuzzing for Java and Solidity compilers.
For JavaScript, Ye et al.~\cite{comfort} presented \textsc{Comfort}, a
compiler fuzzing framework to detect JavaScript engine bugs using ECMAScript
with deep learning-based language models.
Park et al.~\cite{jest} extended $\jiset$ to $\jest$, which performs $N$+1-version differential testing
with $N$ different JavaScript engines and a reference interpreter extracted from ECMAScript.
$\jest$ detects not only engine bugs but also specification bugs in
ECMAScript using the cross-referencing oracle.  However, it requires multiple JavaScript engines and
takes dozens of hours to test a version of ECMAScript.
Instead, $\tool$ can detect specification bugs without JavaScript engines in less than five minutes.
Because $\tool$ uses abstract semantics while $\jest$ uses concrete semantics,
$\tool$ can quickly analyze more semantics than $\jest$.

>>>>

\paragraph{JavaScript Tools}
ECMAScript is the standard language specification for JavaScript maintained by
TC39.  In late 2014, the committee announced
its plan to release ECMAScript annually and adopt the open development process
to quickly adapt to evolving development environments.  Various JavaScript engines such
as Google V8~\cite{v8}, GraalJS~\cite{graaljs}, QuickJS~\cite{qjs}, and Moddable
XS~\cite{moddable} should conform to the syntax and semantics described in
annually updated ECMAScript.  Beyond JavaScript engines, diverse
research projects use JavaScript specifications.  The main research direction
has been static analyzers such as JSAI~\cite{jsai}, SAFE~\cite{safe},
TAJS~\cite{tajs}, and WALA~\cite{wala} based on the abstract interpretation
framework~\cite{ai1977, ai1992} with their own analysis techniques.
They defined abstract semantics of the JavaScript semantics described in ECMAScript to statically
analyze JavaScript programs in a finite time.
Chargu{\'e}raud et al.~\cite{jsexplain} presented JSExplain, a debugger for JavaScript, by
implementing a reference interpreter in OCaml following the algorithm steps in ECMAScript closely.
For a given JavaScript program, the debugger interactively produces execution traces
investigated in a browser, with an interface that displays the
JavaScript code and the interpreter's state.
Fragoso Santos et al.~\cite{javert} introduced JaVerT, a JavaScript verification toolchain, based
on the separation logic with an intermediate goto language JSIL.
JaVerT 2.0~\cite{javert2} extends it to support compositional symbolic execution
for JavaScript based on bi-abduction.  However, because all of them manually handle
ECMAScript with their own intermediate representations, most of them still 
target ES5.1 released in 2011 instead of the latest one.

\paragraph{Mechanized Specification Extraction}
Researchers in various application domains have extracted mechanized specifications from
specifications written in natural languages to handle the contents in the specifications automatically.
For system architectures, researchers utilized Natural
Language Processing (NLP) and Machine Learning techniques to extract formal semantics
of small-sized low-level assembly languages for x86~\cite{x86} and ARM~\cite{arm}.
For Java API functions, Zhai et al.~\cite{javadoc} presented a
technique to automatically extract models from their documentation using NLP techniques.
For the JavaScript programming language, Park et al.~\cite{jiset}
presented $\jiset$, a tool that extracts a mechanized specification from ECMAScript.
While all the previous JavaScript formal semantics~\cite{lambdajs, jscert,
kjs} were manually defined, $\jiset$ automatically extracts formal semantics directly from ECMAScript.
We utilized $\jiset$ to analyze 864 ECMAScript versions via $\tool$.

\paragraph{Specification-based Testing}
Recently, researchers have utilized specifications to test their implementations.
For network protocols, Kim et al.~\cite{basespec} proposed a novel approach named
\textsc{BaseSpec}, which extracts message structures from tables in cellular
specifications for L3 protocols to perform comparative analysis of baseband software.
Schumi and Sun~\cite{spectest} presented SpecTest, which utilized an
executable language semantics to perform fuzzing for Java and Solidity compilers.
For JavaScript, Ye et al.~\cite{comfort} presented \textsc{Comfort}, a
compiler fuzzing framework to detect JavaScript engine bugs using ECMAScript
with deep learning-based language models.
Park et al.~\cite{jest} extended $\jiset$ to $\jest$, which performs $N$+1-version differential testing
with $N$ different JavaScript engines and a reference interpreter extracted from ECMAScript.
$\jest$ detects not only engine bugs but also specification bugs in
ECMAScript using the cross-referencing oracle.  However, it requires multiple JavaScript engines and
takes dozens of hours to test a version of ECMAScript.
Instead, $\tool$ can detect specification bugs without JavaScript engines in two minutes.
Because $\tool$ uses abstract semantics while $\jest$ uses concrete semantics,
$\tool$ can quickly analyze more scope of semantics than $\jest$.
